sem

### 2022-12-12 scripts/workshop/sem.Rmd
with direct effect temp

Using lagged data
```{r}
lagged_cc_temp <- lm(lag_cc ~ lag_temp, data = clean)
lagged_size_temp <- lm(log10(lag_size) ~ lag_temp + lag_cc, data = clean)
lagged_prev_cc <- lm(Prevalence ~ lag_cc + log10(lag_size), data = clean)
lagged_prev_temp_cc <- glm(Prevalence ~ lag_cc + log10(lag_size) + lag_temp, data = clean)

@@

>>>>

Using lagged data
```{r}
lagged_cc_temp <- lm(lag_cc ~ lag_temp, data = clean)
lagged_size_temp <- lm(log10(lag_size) ~ lag_temp + lag_cc, data = clean)
lagged_prev_cc <- lm(Prevalence ~ lag_cc + log10(lag_size), data = clean)
lagged_prev_temp_cc <- lm(Prevalence ~ lag_cc + log10(lag_size) + lag_temp, data = clean)

@@

```{r}
summary(sem_1_lagged)
plot(sem_1_lagged)
plot(sem_1_lagged, return = T)
```
